Locally-Oriented Programming: A simple programming model for stencil computations

### 2015-01-23 papers/LOPe/motivation.tex
Added first paragraph to motivation section.

>>>>

The concepts in this paper were motivated by problems encountered during
the development of PetaVision, a C++ software framework designed for simulating
large networks of spiking neurons in the visual cortex of primates.  PetaVision
was designed to run on massively parallel hardware architectures and a primitive
version of PetaVision achieved over a Petaflop/s of sustained single precision
performance on Roadrunner, the fastest computer in the world for a brief
period of time.

Describe neural layers, spiking neurons, synaptic connections, weights,
and plasticity.  Reference Heubel.

Give a simple 1D (cartoon) example of connections within a neural network in
Figure 1.  Describe the size of visual cortex in terms of the number of neurons,
the number of synaptic connections, and performance.  Reference SC Gorden Bell
paper from IBM.
